02-deseq2-sextissuespecific

### 2019-03-14 scripts/02-DESeq2-sextissuespecific.Rmd
rename for order

---
title: "01-deseq2-all"
output: html_document
---

@@

Now, I'll do RNAseq on all the data from the parental care characterization study.

@@

>>>>

---
title: "02-deseq2-sextissuespecific"
output: md_document
---

@@

Now, I'll do RNAseq on all the data from the parental care characterization study for each tissue and sex.

@@

```{r}

colData$sextissue <- as.factor(paste(colData$sex, colData$tissue, sep = ""))

mygroups <- levels(colData$sextissue)

for(i in mygroups){
  print(i)
  colData <- colData %>%
    dplyr::filter(grepl(i, sextissue)) %>%
    droplevels()
  row.names(colData_characterization) <- colData_characterization$V1
  colData <- 
  print(head(colData_characterization))
}

# print sample sizes
colData_characterization %>% select(sex,treatment, tissue)  %>%  summary()

savecols <- as.character(colData_characterization$V1) 
savecols <- as.vector(savecols) 
countData_characterization <- countData %>% dplyr::select(one_of(savecols))

# check that row and col lenghts are equal
ncol(countData_characterization) == nrow(colData_characterization)
}
```
